---
title: "ICPhS analysis"
author: "Xinyu Zhang"
date: '2023-01-21'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Preprocessing: 
writing a function to code in phoneme contrast according to word pair, steps on continuum according to audio file name, response vowel according to left/right button 
```{r, include = FALSE}
library(dplyr)
process <- function(file) {
  subject <- read.csv(file, header = TRUE, sep = ",") %>% 
    select(subject_nr, count_perceptionPretestResponse, count_perceptionPostTestResponse, percepPretestAudio, percepPretestA, percepPretestB, perceptionPostTestAudio, perceptionPostTestOptionA, perceptionPostTestOptionB, response_perceptionPretestResponse, response_perceptionPostTestResponse, title)
  
  percepPre <- subject %>%
    mutate(audio = percepPretestAudio) %>%
    select(count_perceptionPretestResponse, percepPretestA, percepPretestB,response_perceptionPretestResponse, subject_nr, audio, title) %>% 
    slice(c(64:147),)
    
  percepPre <- percepPre %>% 
    mutate(prepost = c(rep ("pre", nrow(percepPre))))
  
  percepPost <- subject %>%
    mutate(audio = perceptionPostTestAudio) %>%
    select(count_perceptionPostTestResponse, perceptionPostTestOptionA, perceptionPostTestOptionB, response_perceptionPostTestResponse, subject_nr, audio, title) %>% 
    slice(c(202:285),)
  
  percepPost <- percepPost %>% 
    mutate(prepost = c(rep ("post", nrow(percepPost))))


binded <- bind_rows(percepPre, percepPost)

binded$subject_nr <- as.character(binded$subject_nr)

processed<- binded %>% 
  mutate(
    contrast = case_when(
      audio == "sik-sec1.wav" ~ "IE",
      audio == "sik-sec2.wav" ~ "IE",
      audio == "sik-sec3.wav" ~ "IE",
      audio == "sik-sec4.wav" ~ "IE",
      audio == "sik-sec5.wav" ~ "IE",
      audio == "sik-sec6.wav" ~ "IE",
      audio == "sik-sec7.wav" ~ "IE",
      audio == "pip-pep_continuumStep_1_stereo.wav" ~ "IE",
      audio == "pip-pep_continuumStep_2_stereo.wav" ~ "IE",
      audio == "pip-pep_continuumStep_3_stereo.wav" ~ "IE",
      audio == "pip-pep_continuumStep_4_stereo.wav" ~ "IE",
      audio == "pip-pep_continuumStep_5_stereo.wav" ~ "IE",
      audio == "pip-pep_continuumStep_6_stereo.wav" ~ "IE",
      audio == "pip-pep_continuumStep_7_stereo.wav" ~ "IE",
      audio == "kik-kek_continuumStep_1_stereo.wav" ~ "IE",
      audio == "kik-kek_continuumStep_2_stereo.wav" ~ "IE",
      audio == "kik-kek_continuumStep_3_stereo.wav" ~ "IE",
      audio == "kik-kek_continuumStep_4_stereo.wav" ~ "IE",
      audio == "kik-kek_continuumStep_5_stereo.wav" ~ "IE",
      audio == "kik-kek_continuumStep_6_stereo.wav" ~ "IE",
      audio == "kik-kek_continuumStep_7_stereo.wav" ~ "IE",
      TRUE ~ "filler"),
      stepOnCon = case_when(
      audio == "sik-sec1.wav" ~ "1",
      audio == "sik-sec2.wav" ~ "2",
      audio == "sik-sec3.wav" ~ "3",
      audio == "sik-sec4.wav" ~ "4",
      audio == "sik-sec5.wav" ~ "5",
      audio == "sik-sec6.wav" ~ "6",
      audio == "sik-sec7.wav" ~ "7",
      audio == "pip-pep_continuumStep_1_stereo.wav" ~ "1",
      audio == "pip-pep_continuumStep_2_stereo.wav" ~ "2",
      audio == "pip-pep_continuumStep_3_stereo.wav" ~ "3",
      audio == "pip-pep_continuumStep_4_stereo.wav" ~ "4",
      audio == "pip-pep_continuumStep_5_stereo.wav" ~ "5",
      audio == "pip-pep_continuumStep_6_stereo.wav" ~ "6",
      audio == "pip-pep_continuumStep_7_stereo.wav" ~ "7",
      audio == "kik-kek_continuumStep_1_stereo.wav" ~ "1",
      audio == "kik-kek_continuumStep_2_stereo.wav" ~ "2",
      audio == "kik-kek_continuumStep_3_stereo.wav" ~ "3",
      audio == "kik-kek_continuumStep_4_stereo.wav" ~ "4",
      audio == "kik-kek_continuumStep_5_stereo.wav" ~ "5",
      audio == "kik-kek_continuumStep_6_stereo.wav" ~ "6",
      audio == "kik-kek_continuumStep_7_stereo.wav" ~ "7",
      TRUE ~ "filler"),
      BB = case_when(
        title == "BB-MN-AF" ~ "BB",
        title == "BB-AF-MN" ~ "BB",
        TRUE ~ "NB"
        ),
      AF = case_when(
        title == "NB-AF-MN" ~ "AF",
        title == "BB-AF-MN" ~ "AF",
        TRUE ~ "MN"
      )
  ) %>% 
  filter(contrast == "IE") %>% 
  mutate(
    responseV = case_when(
      percepPretestA == "sik"&response_perceptionPretestResponse == "A" ~ "I",
      percepPretestB == "sec"&response_perceptionPretestResponse == "E" ~ "E",
      percepPretestA == "pip"&response_perceptionPretestResponse == "A" ~ "I",
      percepPretestB == "pep"&response_perceptionPretestResponse == "E" ~ "E",
      percepPretestA == "kek"&response_perceptionPretestResponse == "A" ~ "E",
      percepPretestB == "kik"&response_perceptionPretestResponse == "E" ~ "I", #previous mistake here
      perceptionPostTestOptionA == "sik"&response_perceptionPostTestResponse == "A" ~ "I",
      perceptionPostTestOptionB == "sec"&response_perceptionPostTestResponse == "E" ~ "E",
      perceptionPostTestOptionA == "pip"&response_perceptionPostTestResponse == "A" ~ "I",
      perceptionPostTestOptionB == "pep"&response_perceptionPostTestResponse == "E" ~ "E",
      perceptionPostTestOptionA == "kek"&response_perceptionPostTestResponse == "A" ~ "E",
      perceptionPostTestOptionB == "kik"&response_perceptionPostTestResponse == "E" ~ "I"  #previous mistake here
      ),
      count = case_when(
        prepost == "pre" ~ count_perceptionPretestResponse,
        prepost == "post" ~ count_perceptionPostTestResponse
      ),
      pair = case_when(percepPretestA == "sik"~ "sik-sec",
                       percepPretestA == "pip" ~ "pip-pep",
                       percepPretestA == "kek" ~ "kik-kek",
                       perceptionPostTestOptionA == "sik" ~ "sik-sec",
                       perceptionPostTestOptionA == "pip" ~ "pip-pep",
                       perceptionPostTestOptionA == "kek" ~ "kik-kek",
        
      )
  )
}
```

run the function on data from subject 1 (which creates a "starting table" with all the correct columns for the rest of the new data to concatenate to)
```{r, include = FALSE}
bigtable <- process("subject-1.csv")
```

run the function on data from subjects 2 to 60, concatenate into a full table
```{r, include = FALSE}
for (n in c(2:60)){
  name <- paste("subject-",n,".csv", sep = '')
  processed<- process(name)
  processed_n <- processed
  subject_n <- processed_n
  bigtable <- bind_rows(bigtable, subject_n)
}

nrow(bigtable)
#write.csv(bigtable, file = "combined2.csv")
```

read in full table
```{r, include = FALSE}
library(lme4)
library(minqa)
bigtable<- read.csv("combined2.csv", sep = ",", header = TRUE)

#steps as numeric variable:
bigtable$stepOnCon <- as.numeric(bigtable$stepOnCon)
```

plotting raw data:
```{r, include = FALSE}
library(dplyr)
#count number of stimuli per step
bigtable %>% 
  count(stepOnCon, responseV) #360

#count for number of stimuli in BB group per step 
bigtable %>%  filter(BB == "BB") %>% 
  count(stepOnCon, responseV) #186

#count for number of stimuli in NB group per step 
bigtable %>%  filter(BB == "NB") %>% 
  count(stepOnCon, responseV) #174

#count for number of stimuli in pretest in BB group per step
bigtable %>%  filter(BB == "BB", prepost == "pre") %>% 
  count(stepOnCon, responseV) #93

#count for number of stimuli in posttest in BB group per step
bigtable %>%  filter(BB == "BB", prepost == "post") %>% 
  count(stepOnCon, responseV) #93

#count for number of stimuli in pretest in NB group per step
bigtable %>%  filter(BB == "NB", prepost == "pre") %>% 
  count(stepOnCon, responseV) #87

#count for number of stimuli in posttest in NB group per step
bigtable %>%  filter(BB == "NB", prepost == "post") %>% 
  count(stepOnCon, responseV) #87

#count for numner of stimuli in pretest in AF group per step
bigtable %>%  filter(AF == "AF", prepost == "pre") %>% 
  count(stepOnCon, responseV) #90
#count for number of stimuli in posttest in AF group per step
bigtable %>%  filter(AF == "AF", prepost == "post") %>% 
  count(stepOnCon, responseV) #90
#count for number of stimuli in pretest in MN group per step
bigtable %>%  filter(AF == "MN", prepost == "pre") %>% 
  count(stepOnCon, responseV)#90
#count for number of stimuli in posttest in MN group per step
bigtable %>%  filter(AF == "MN", prepost == "post") %>% 
  count(stepOnCon, responseV)

#actual percentage of E responses
bbprepost <- bigtable %>%
  filter(responseV == "E") %>% 
  dplyr::count(stepOnCon, responseV, BB, prepost)%>% 
  mutate(
    proportionE = case_when(
      BB == "NB" ~ n/87,
      BB == "BB" ~ n/93)
  )

```


```{r}
library(ggplot2)
ggplot(bbprepost,aes( x=stepOnCon, y=proportionE,color=BB,lty=prepost)) + geom_point( aes(shape = prepost), size = 2) + geom_line() + theme_bw() + scale_color_manual(values = c("#440154FF", "#22A884FF"))
#+ scale_color_grey()
#+ 
#+ icphs colors: values = c("#440154FF", "#22A884FF")
#+ radboud colors: values = c("#ff424b", "#730e04")

#ggsave(file="prepostBB.png")


ggplot(bbprepost,aes( x=stepOnCon, y=proportionE,color=BB,lty=prepost, shape = prepost)) + geom_point() + stat_smooth(method="glm", se=FALSE,
                method.args = list(family=binomial)) + theme_bw() + scale_color_viridis_d()
```


```{r}
bbstep <- bigtable %>%
  filter(responseV == "E") %>% 
  dplyr::count(stepOnCon, responseV, BB)%>% 
  mutate(
    proportionE = case_when(
      BB == "NB" ~ n/87,
      BB == "BB" ~ n/93)
  )

library(ggplot2)
ggplot(bbstep,aes( x=stepOnCon, y=proportionE,color=BB)) + geom_point() + geom_line() + theme_bw()+scale_color_manual(values=c("#FDE725FF", "#440154FF"))

#ggsave(file="stepBB.png")
```



bar plot:
```{r}
library(dplyr)
library(ggplot2)
library(viridis)
#filtering for step4
bbprepost4 <- bigtable %>%
  filter(responseV == "E", stepOnCon == 4) %>% 
  dplyr::count(stepOnCon, responseV, BB, prepost) %>% 
  mutate(percentE = case_when(
      BB == "BB" ~ n/93,
      BB == "NB" ~ n/87))

bbprepost4

#bbprepost4 <-bbprepost %>% mutate(percentE = n/90)

bbprepost4$BB <- factor(bbprepost4$BB,
                          levels = c("NB", "BB"))
bbprepost4$prepost <- factor(bbprepost4$prepost,
                          levels = c("pre", "post"))

plot <- ggplot(bbprepost4, aes(x= prepost, y= percentE, fill = BB)) +
  geom_bar(stat="identity", position = "dodge")+
  scale_y_continuous(labels=scales::percent, limits = c(0, 1))+
  labs (y = "percentage of /ɛ/ responses", x = "*at continuum step 4") + theme_classic()

#plot + scale_fill_viridis_d()
plot + scale_fill_manual(values=c("#ff424b", "#730e04"))
#radboud colors: col = c("#ff424b", "#730e04")
#ggsave("barchart_step4Corrected.png")
```

#### bar plot for auditory feedback
```{r}
afprepost4 <- bigtable %>%
  filter(responseV == "E", stepOnCon == 4) %>% 
  dplyr::count(stepOnCon, responseV, AF, prepost) %>% 
  mutate(percentE = case_when(
      AF == "AF" ~ n/90,
      AF == "MN" ~ n/90))

afprepost4$AF <- factor(afprepost4$AF,
                          levels = c("AF", "MN"))
afprepost4$prepost <- factor(afprepost4$prepost,
                          levels = c("pre", "post"))

plot <- ggplot(afprepost4, aes(x= prepost, y= percentE, fill = AF)) +
  geom_bar(stat="identity", position = "dodge")+
  scale_y_continuous(labels=scales::percent, limits = c(0, 1))+
  labs (y = "percentage of /ɛ/ responses", x = "*at continuum step 4") + theme_classic()

#plot + scale_fill_viridis_d()
plot + scale_fill_manual(values=c("#ff424b", "#730e04"))
#radboud colors: col = c("#ff424b", "#730e04")
#ggsave("MNbarchart_step4.png")
```


#### model selection by ANOVA

####code contrasts for responses as 0 vs 1
```{r}
library(dplyr)
bigtable<- bigtable %>% 
  mutate(
    responseE = case_when(
      responseV == "I" ~ 0,
      responseV == "E" ~ 1)
  )
bigtable$responseE <- as.factor(bigtable$responseE)
```


#### coding in the treatment contrast levels
```{r}
#NB, AF, and pretest as reference levels
bigtable$BB <- as.factor(bigtable$BB)
bigtable$BB <- relevel(bigtable$BB, ref = "NB")

bigtable$AF <- as.factor(bigtable$AF)
bigtable$AF <- relevel(bigtable$AF, ref = "AF")

bigtable$prepost <- as.factor(bigtable$prepost)
bigtable$prepost <- relevel(bigtable$prepost, ref = "pre")

#Centering the StepOnCon variable
bigtable$cstep <- bigtable$stepOnCon - 4


```

#### starting with the four-way interaction model
```{r}
library(lme4)
model1 <- glmer(responseE~ cstep * prepost * AF * BB + (1|subject_nr) + (1|pair),data = bigtable, family=binomial(link="logit"),
            control=glmerControl(optimizer="bobyqa"))
summary(model1)
```

removing the least significant interaction (cstep:prepost:AF:BB), which leaves out all four-way interactions. Hence adding up all possible three-way interactions.

all possible combinations:
```{r}
combn(c("cstep", "prepost", "AF", "BB"), 3)
```

adding them up
```{r}
model2 <- glmer(responseE~ cstep *prepost * AF +cstep *prepost * BB + cstep *AF * BB+ prepost *AF * BB + (1|subject_nr) + (1|pair), data = bigtable, family=binomial(link="logit"),
            control=glmerControl(optimizer="bobyqa"))
```

compare model1 and model2
```{r}
anova(model1, model2, REML = FALSE)
```

not significantly different. Now check the output of model1 to take out the least sig. effect

```{r}
summary(model2)
```

the most insignificant one is prepost:AF, but starting from the higher order ones first and take out the most insignificant 3-way interaction (cstep:prepost:BB), and compare the model with the previous one

```{r}
model3 <- glmer(responseE~ cstep *prepost * AF + cstep *AF * BB+ prepost *AF * BB + (1|subject_nr) + (1|pair), data = bigtable, family=binomial(link="logit"),
            control=glmerControl(optimizer="bobyqa"))

anova (model2, model3, REML = FALSE)
```

not significant. Now check the output of the new model to take out the least sig. 3-way interaction

```{r}
summary(model3)
```

most insig. 3-way is prepost:AF:BB, But adding back some of the two-way interactions that will be removed due to the removal of this three-way. Compare new model with the previous one

```{r}
model4 <- glmer(responseE~ cstep *prepost * AF + cstep *AF * BB+ prepost * BB + AF * BB + (1|subject_nr) + (1|pair), data = bigtable, family=binomial(link="logit"),
            control=glmerControl(optimizer="bobyqa"))

anova (model3, model4, REML = FALSE)
```

not significant, and both AIC and BIC decreased, thus adopting the new model.
Check model summary to remove the least significant 3-way
```{r, include = FALSE}
summary(model4)
```

removing cstep:prepost:AF, model becomes $responseE$ ~ $cstep *AF * BB+ (1|subject_nr) + (1|pair)$. But *prepost* is now completely removed but there were important two way interactions involving prepost. So also adding in the two-ways that appeared in the previous models.
and compare the new model with the previous one
```{r, include = FALSE}
model5 <- glmer(responseE~ cstep *BB * AF+ BB*prepost + AF * BB + cstep * prepost + prepost * AF + (1|subject_nr) + (1|pair), data = bigtable, family=binomial(link="logit"),
            control=glmerControl(optimizer="bobyqa"))

anova (model4, model5, REML = FALSE)
```

not significant(but almost, and AIC and BIC don't vary much between the two models) . Print out model summary for model5 to remove the least significant interaction:
```{r}
summary(model5)
```
The least significant effect now is cstep:prepost, but there are higher order contrasts (cstep:AF:BB) that are significant and shouldn't be removed. 

Try removing cstep:prepost:
```{r}
model6 <- glmer(responseE~ cstep *AF * BB+ prepost * BB + AF * BB + prepost * AF + (1|subject_nr) + (1|pair), data = bigtable, family=binomial(link="logit"),
            control=glmerControl(optimizer="bobyqa"))


anova (model5, model6, REML = FALSE)
```

Model6 is different from Model5. Selecting model 5.

plotting model residuals
```{r}
plot(density(resid(model5)),main='Distribution of residuals')

qqnorm(resid(model5)); qqline(resid(model5))
```

#### Interpretation

significant effects: cstep, BB, cstep:BB, BB:prepost, cstep:AF:BB

cstep 1.95298: at pretest, in the NB x AF group, as cstep increases by 1, the odds of an E response changes by exp(1.95298) = `r exp(1.95298)`.

BB -1.59338: at pretest, under AF condition, on step 4 (when cstep = 0, the intercept), the odds of an E response changes in the BB group by exp(-1.59338) = `r exp(-1.59338)`, as compared to the NB group.

cstep:BBBB -0.65283: at pretest, under AF condition, when cstep increase by 1, in the BB group, the odds of an E response changes by exp(-0.65283) = `r exp(-0.65283)`.


BBBB:prepostpost 0.60986: on step 4 (when cetep = 0, the intercept), under AF condition, in the BB group, the odds of an E response changes in the posttest by exp(0.60986) = `r exp(0.60986)`

cstep:AFMN:BBBB 0.73318: at pretest, in the MN x BB group, when step increase by 1, the odds of an E response changes by exp(0.73318) = `r exp(0.73318)`.

```{r,, include = FALSE}
logit2prob <- function(logit){
  odds <- exp(logit)
  prob <- odds / (1 + odds)
  return(prob)
}
logit2prob(0.73318)
```



using the Effects package to list out the probability of an E response as cstep increases:
```{r}
library(effects)
effect('cstep', model5)
```
In NB group, at pretest, the probability of E responses increases as cstep increases

Same for the effects of BB, cstep:BB, BB:prepost, cstep:AF:BB:
```{r}
effect('BB', model5)
effect('cstep:BB', model5)
effect('BB:prepost', model5)
ef<-effect('cstep:BB:AF', model5)
```

plotting the effects as probabilities:
```{r}
effectsTheme(col = "colorblind")
plot(effect('BB', model5), multiline = TRUE)

plot(effect('cstep', model5), multiline = TRUE)

plot(effect('cstep:BB', model5), multiline = TRUE)

plot(effect('BB:prepost', model5), multiline = TRUE)

lattice::trellis.par.set(effectsTheme(col = c("#ff424b", "#730e04")))
plot(effect('cstep:BB:AF', model5),multiline = TRUE, main=paste(""), axes=list(y=list(lab={"responseE (logit)"})))

#radboud colors: col = c("#ff424b", "#730e04")
#icphs colors: col = c("#440154FF", "#22A884FF")

```

plotting BB and prepost, reversing the x-axis and factor labels

```{r}
reverse <- effect('BB:prepost', model5)
write.csv(reverse, "reverse.csv", row.names=FALSE, quote=FALSE) 
```

```{r}
library(ggplot2)
ggplot(as.data.frame(reverse), aes(x= prepost, y= fit, color = BB, group = BB)) +
  geom_point()+ geom_line()+theme_classic() + ylab("responseE (logit)")
```

plotting BB and step, reversing the x-axis and factor labels




plotting model on top of data:

```{r}
library(ggplot2)

#re-summarizing data
bbstep <- bigtable %>%
  filter(responseV == "E") %>% 
  dplyr::count(stepOnCon, responseV, BB)%>% 
  mutate(
    proportionE = case_when(
      BB == "BB" ~ n/(93*2),
      BB == "NB" ~ n/(87*2))
  )



raw<- ggplot()+ 
  geom_point(data=bbstep, aes(x = stepOnCon, y = proportionE, color = BB)) +
  geom_line(data=bbstep, aes(x = stepOnCon, y = proportionE, color=BB))

model_plot <- effect("cstep:BB", model5)
model_plot <-as.data.frame(model_plot) #saving it as a data frame
model_plot$step <- model_plot$cstep + 4 #uncentering step to match the x-scale on the raw data plot


raw + 
  #geom_ribbon(data = model_plot, aes(x= step, ymin = lower, ymax = upper, fill = BB), alpha = 0.15)+ scale_color_viridis_d()+ #ribbon = error bar, 
  #geom_point(data=model_plot,aes(x = step, y = fit, color = BB), alpha = 1)+
  geom_line(data=model_plot,aes(x = step, y = fit, color = BB),linetype = "dotdash", lwd=0.6, alpha = 1)+
  scale_x_continuous("Continuum step")+
  scale_y_continuous("E response")+theme_bw() + scale_color_viridis_d()+
  ggtitle("model in solid line, data in dotdash")
  
#ggsave(file = "dataAndModel.png")

```

model plot:

```{r}
ggplot()+
  geom_line(data=model_plot,aes(x = step, y = fit, color = BB), lwd=0.6, alpha = 1)+
  scale_x_continuous("Continuum step")+
  scale_y_continuous("E response")+theme_bw() + scale_color_viridis_d()
#ggsave(file = "modelPlot.png")
```




Relevel so that the BB group is the reference level, to check whether the BB group differ between pre- and post-test
```{r}
#BB, AF, and pretest as reference levels
bigtable$BB <- as.factor(bigtable$BB)
bigtable$BB <- relevel(bigtable$BB, ref = "BB")

bigtable$AF <- as.factor(bigtable$AF)
bigtable$AF <- relevel(bigtable$AF, ref = "AF")

bigtable$prepost <- as.factor(bigtable$prepost)
bigtable$prepost <- relevel(bigtable$prepost, ref = "pre")

#Centering the StepOnCon variable
bigtable$cstep <- bigtable$stepOnCon - 4

```

Rerun the same final model:
```{r}
library(lme4)
model5 <- glmer(responseE~ cstep *BB * AF+ BB *prepost + AF * BB + cstep * prepost + prepost * AF + (1|subject_nr) + (1|pair), data = bigtable, family=binomial(link="logit"),
            control=glmerControl(optimizer="bobyqa"))

summary(model5)
```
Cannot conclude that BB group differ in their behavior between pretest and posttest.

plotting effects:
```{r}
library(effects)
effect('cstep', model5)
effect('BB', model5)
effect('cstep:BB', model5)
effect('BB*prepost', model5)
effect('cstep:BB:AF', model5)
effectsTheme(col = "colorblind")
plot(effect('BB', model5), multiline = TRUE)

plot(effect('cstep', model5), multiline = TRUE)
plot(effect('prepost', model5), multiline = TRUE)

plot(effect('cstep:AF', model5), multiline = TRUE)

plot(effect('BB:prepost', model5), multiline = TRUE)

plot(effect('cstep:BB:AF', model5), multiline = TRUE)

```


Relevel so that posttest is reference level, to check whether at posttest BB and NB group differ:

```{r}
#NB, AF, and posttest as reference levels
bigtable$BB <- as.factor(bigtable$BB)
bigtable$BB <- relevel(bigtable$BB, ref = "NB")

bigtable$AF <- as.factor(bigtable$AF)
bigtable$AF <- relevel(bigtable$AF, ref = "AF")

bigtable$prepost <- as.factor(bigtable$prepost)
bigtable$prepost <- relevel(bigtable$prepost, ref = "post")

#Centering the StepOnCon variable
bigtable$cstep <- bigtable$stepOnCon - 4

```

Rerun the same final model:
```{r}
model5 <- glmer(responseE~ cstep *BB * AF+ prepost * BB + AF * BB + cstep * prepost + prepost * AF + (1|subject_nr) + (1|pair), data = bigtable, family=binomial(link="logit"),
            control=glmerControl(optimizer="bobyqa"))

summary(model5)
plot(effect('cstep:BB:AF', model5), multiline = TRUE)
```

AF and BB are both somewhat significant. 

Interpretation:

AFMN  -1.11464: Under NB condition, at posttest, the odds of MN group giving an E response differ by exp(-1.11464) = `r exp(-1.11464)` compared to the AF group.

BBBB -0.98353: at posttest, on step 4, in the AF condition, the odds of an E response in the BB group differ by exp(-0.98353) = `r exp(-0.98353)`.

cstep:BBBB -0.65283: at posttest, under AF condition, the odds of an E response in the BB group changes by exp(-0.65283) = `r exp(-0.65283)` as cstep increases by 1.

The values in BBBB:prepostpost and cstep:AFMN:BBBB are the same when pretest, NB, AF were the reference levels.


```{r, include = FALSE}
model6 <- glmer(responseE~ prepost * BB + AF * BB + cstep * prepost + prepost * AF + cstep * AF + cstep *BB + (1|subject_nr) + (1|pair), data = bigtable, family=binomial(link="logit"),
            control=glmerControl(optimizer="bobyqa"))

anova (model5, model6, REML = FALSE)
```

```{r, include = FALSE}
bigtable %>% filter(BB == 'BB', prepost == "post") %>% 
  group_by(subject_nr) %>% 
  summarize()
```


```{r}
library(ggplot2)
#boxplot for pre
pre <- bbprepost %>% 
  filter(prepost == "pre")

p <- ggplot(data=pre,aes(x = stepOnCon, y = proportionE, group = stepOnCon, color = BB))+ 
    scale_x_continuous("Continuum step")+
    scale_y_continuous("E proportion")+
    theme_classic()+ 
    theme(text = element_text(size = 15), axis.text.x = element_text(size=10), legend.text = element_text(size = 15)) 

p + geom_boxplot() + ggtitle("perception at pretest") 

#boxplot for post
post <- bbprepost %>% 
  filter(prepost == "post")

p <- ggplot(data=post,aes(x = stepOnCon, y = proportionE, group = stepOnCon, color = BB))+ 
    scale_x_continuous("Continuum step")+
    scale_y_continuous("E proportion")+
    theme_classic()+ 
    theme(text = element_text(size = 15), axis.text.x = element_text(size=10), legend.text = element_text(size = 15)) 

p + geom_boxplot() + ggtitle("perception at posttest")

#collapsed over all four conditions
p <- ggplot(data=bbprepost,aes(x = stepOnCon, y = proportionE, group = stepOnCon, color = BB))+ 
    scale_x_continuous("Continuum step")+
    scale_y_continuous("E proportion")+
    theme_classic()+ 
    theme(text = element_text(size = 15), axis.text.x = element_text(size=10), legend.text = element_text(size = 15)) 

p + geom_boxplot() + ggtitle("perception collapsed over pre- and posttest and all conditions")


#tabbed <- bigtable %>% filter(BB == "BB", prepost == "pre", responseV == "E") %>% 
  #group_by(subject_nr, stepOnCon, responseV) %>%
  #ungroup()%>% 
  #count(subject_nr, stepOnCon, responseV) #%>% 

#head(tabbed)


```


