---
title: "Bayesian analysis on perception data"
output: html_notebook
---

Reading in data: 

```{r}
perc <- read.csv("combined2.csv", sep = ",", header = TRUE)
```


checking data types:

```{r}
head(perc)
summary(perc)
```

continuum step should be numeric

subject number should be strings

prepost should be factors

pair should be factors

responseV should be factors

BB should be factors

AF should be factors

Adjusting accordingly:

```{r}
perc$stepOnCon <- as.numeric(perc$stepOnCon)

perc$subject_nr <- as.character(perc$subject_nr)

perc$prepost <- as.factor(perc$prepost)

perc$pair <- as.factor(perc$pair)

perc$responseV <- as.factor(perc$responseV)

perc$BB <- as.factor(perc$BB)

perc$AF <- as.factor(perc$AF)
```


```{r}
library(dplyr)
perc<- perc %>% 
  mutate(
    responseE = case_when(
      responseV == "I" ~ 0,
      responseV == "E" ~ 1)
  )
perc$responseE <- as.factor(perc$responseE)
```


#### coding in the treatment contrast levels
```{r}
#NB, AF, and pretest as reference levels
perc$BB <- relevel(perc$BB, ref = "NB")

perc$AF <- relevel(perc$AF, ref = "AF")

perc$prepost <- relevel(perc$prepost, ref = "pre")

#Centering the StepOnCon variable
perc$cstep <- perc$stepOnCon - 4

```

# Basic multivariate

```{r}
library(brms)

model1 <- responseE~ cstep * prepost * AF * BB + (1|subject_nr) + (1|pair)

fit1 <- brm(model1, data = perc,family = bernoulli(), seed = 446) #setting seed for reproducibility
```

Plot trace and density:

```{r}
plot(fit1)
```

posterior predictive check:

```{r}
pp_check(fit1)
```


summarizing the results:

```{r}
summary(fit1)
```

Check $R^2$

```{r}
bayes_R2(fit1)
```

